\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-07-09 paper.tex
Make the scope of the article clear
(knowledge for integration, no literature review, no novelty at component levels)

\subsection{Deployment on robots}

While we do not present experiments in this paper, the ideas and techniques we
present all have been implemented and tested on several robots (see previously
reported experiments in~\cite{Lemaignan2010, Ros2010b, Lemaignan2011a,
Warnier2012a}). Also, videos presenting some of these experimental results can
be watched online at~\url{http://www.laas.fr/~slemaign}.

>>>>

\subsection{Scope of the article}

In essence, this article portrays our use of \emph{explicit semantic
interfaces} to integrate several deliberative components into a decisional
architecture for our robots. It reports on our experience with acquiring,
managing and reusing grounded knowledge in the context of human-robot
interaction.

Unlike previous publications by the authors~\cite{Pandey2011, Lemaignan2010,
Ros2010b, Lemaignan2011a, Warnier2012a, Alami2011, Sisbot2011, Alili2009} that
introduced the deliberative modules of our robots independently from each
others, this contribution is an account of the importance of explicit knowledge
manipulation when \emph{integrating} them into a large cognitive architecture.

While we do not present experiments in this paper, the ideas and techniques we
present all have been implemented and tested on several robots (see previously
reported experiments in~\cite{Lemaignan2010, Ros2010b, Lemaignan2011a,
Warnier2012a}). Videos presenting some of these experimental results can
be watched online at~\url{http://www.laas.fr/~slemaign}.

Also note that this paper does not provide extensive review of existing
literature. We kindly refer the reader to the aforementioned articles for
in-depth discussion of related works in the different fields of cognitive
architectures for robots.
